An Infinite de Bruijn Sequence

### 2016-12-25 paper.tex
...

While our main focus is on analyzing the reversed word, we also have a result about the prefer-max sequence itself. Our result gives the first (to our knowledge) efficient construction for that sequence:

@@

Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word.

>>>>

In particular, the above theorem says that the sequence generated by Algorithm~\ref{inf-construction} is a de Bruijn sequence, i.e., that each word in $\N^n$ appears exactly once as a substring.

While our main focus is on analyzing the reversed sequence, we also have a result about the prefer-max sequence itself. Our result gives the first (to our knowledge) efficient construction for that sequence:

@@

Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word.

\begin{theorem}
	The sequence generated by Algorithm~\ref{efficient-pref-max} is the prefer-max sequence with parameters $k$ and $n$.
\end{theorem}

The main tool that brought us to the above results is a formulation of an alternative description of the infinite sequence. For this, we need to introduce some language.

The de Bruijn graph
